Peer influences in air travel behavior: A social autoregressive analysis

### 2017-07-21 article/article.Rmd
Update packages and modernize to restart

---
title: "Peer influences in air travel behavior: A social autoregressive analysis"
author: Gregory S. Macfarlane, Thomas A. Wall, Bingling Zhang, and Kari E. Watkins
bibliography: bibliography/bibliography.bib
csl: bibliography/elsevier-harvard.csl 
output:
  html_document:
    fig_caption: yes
    theme: journal
    number_sections: yes
---
```{r setup}
library(knitr) # nice output tables

# knit options
opts_chunk$set(
  cache = TRUE, cache.path = "./.cache/",
  echo = TRUE, 
  fig.keep = TRUE, fig.path = "./.figs/"
)

library(dplyr, warn.conflicts = FALSE) # super data wrangling
library(tidyr)
library(igraph) # graph analysis
library(networkD3) # interactive graph visualizer
```

@@

```{r load_user, warning=FALSE, cache = FALSE}
source("../rscripts/datacleaner.R")
```

@@

```{r save_as_matrices}
# make graph
user_graph <- graph.data.frame(friend_connections)

# export graph edges as adjacency matrix
matrix_list <- list()
for(i in names(friend_connections)[-(1:2)]){
  mat <- as.matrix(get.adjacency(user_graph, type = "both", i))
  # force matrix to be symmetric
  matrix_list[[i]] <- pmax(mat, t(mat))
}
```

>>>>

---
title: "Peer influences in air travel behavior: A social autoregressive analysis"
author: Gregory S. Macfarlane, Thomas A. Wall, Bingling Zhang, and Kari E. Watkins
bibliography: bibliography/bibliography.bib
csl: bibliography/elsevier-harvard.csl 
output:
  html_document:
    fig_caption: yes
    theme: journal
    number_sections: yes
---
```{r setup}
library(knitr) # nice output tables
library(here)

# knit options
opts_chunk$set(
  cache = TRUE, cache.path = ".cache/",
  echo = TRUE, 
  fig.keep = TRUE, fig.path = ".figs/"
)

@@

```{r load_user, warning=FALSE, cache = FALSE}
source(here("rscripts/datacleaner.R"))
```

@@

```{r save_as_matrices}
# make graph
user_graph <- igraph::graph.data.frame(friend_connections)

# export graph edges as adjacency matrix
matrix_list <- list()
for(i in names(friend_connections)[-(1:2)]){
  mat <- as.matrix(igraph::get.adjacency(user_graph, type = "both", i))
  # force matrix to be symmetric
  matrix_list[[i]] <- pmax(mat, t(mat))
}
```
